\textbf{AprilTrack: A Particle-Filter based AprilTag Tracker}

### 2017-01-31 paper/paper.tex
Fixed footnote and regenerated pdf

\textbf{Particle Filters.}\footnote{A more in-depth discussion of particle filters can found in . This } In this regard, particle filters attempt to approximate the posterior distribution at time $t-1$, $p(\vec{x}_{0:t-1}|\vec{z}_{1:t-1})$, using Monte-Carlo methods. A particle filter consists of a set of $N$ samples $\{ (\vec{x}^i_{t-1}, w^i_{t-1}) \}_{i=1}^N$ drawn from the proposal distribution $q(\vec{x}^i)$ and weighted so as to take into account any discrepancy between $q(\vec{x})$ and $p(\vec{x})$ in that $w^i_t \propto p(\vec{x}^i_{0:t}|\vec{z}_{1:t})/q(\vec{x}^i_{0:t}|\vec{z}_{1:t})$.

>>>>

\textbf{Particle Filters.}\footnote{A more in-depth discussion of particle filters can found in \citep{ParticleNotes}. Much of the notation used in \citep{ParticleNotes} is similar to that used here.} In this regard, particle filters attempt to approximate the posterior distribution at time $t-1$, $p(\vec{x}_{0:t-1}|\vec{z}_{1:t-1})$, using Monte-Carlo methods. A particle filter consists of a set of $N$ samples $\{ (\vec{x}^i_{t-1}, w^i_{t-1}) \}_{i=1}^N$ drawn from the proposal distribution $q(\vec{x}^i)$ and weighted so as to take into account any discrepancy between $q(\vec{x})$ and $p(\vec{x})$ in that $w^i_t \propto p(\vec{x}^i_{0:t}|\vec{z}_{1:t})/q(\vec{x}^i_{0:t}|\vec{z}_{1:t})$.
